Verifying Demonstrations

### 2018-02-26 paper/RelatedWork.tex
references for urbancount, divote

Another related approach based on devices is \citet{UrbanCount} which
uses epidemic spreading of crowd-size estimates by device-to-device
communication to count crowds in dense urban environments with high
node mobility and churn. There is, however, no consideration of a potentially
adverserial setting and thus no verification or checks on
eligibility. \citet{DiVote}, a prior work by the same authors for
polling in dense areas, avoids double counting but again only for
honest participants.

>>>>

Another related approach based on devices is UrbanCount~\cite{UrbanCount} which
uses epidemic spreading of crowd-size estimates by device-to-device
communication to count crowds in dense urban environments with high
node mobility and churn. There is, however, no consideration of a potentially
adverserial setting and thus no verification or checks on
eligibility. DiVote~\cite{DiVote}, a prior work by the same authors for
polling in dense areas, avoids double counting but again only for
honest participants.
